HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
Edits to Section 2

Scalability is addressed by employing automatic and semi-automatic approximations of human
judgements. Commonly, such scores decompose over the sub-parts of
the translation, and quantify how many of these sub-parts appear in a manually created reference translation.
This decomposition allows system developers
to localize the errors, or at least unconfirmed parts within the translation.
The most commonly used measures decompose over n-grams or individual words, e.g., 
BLEU \parcite{Papineni:2002}, NIST \parcite{Doddington:2002} and METEOR
\parcite{Banerjee:2005}.
Another common approach is to determine the similarity between the reference and translation
by applying string edit distance \parcite{snover2006study}.
While these measures stimulated much progress in MT research by allowing
the evaluation of massive-scale experiments, the focus on words and n-grams does
not provide a good estimate of semantic correctness, and may favour shallow string-based
MT models.

@@

Perhaps the most notable attempt at semantic MT evaluation is MEANT and
its human variant HMEANT \parcite{lo2011structured}, which quantifies the similarity between
the reference and translation in terms of the overlap in
their verbal argument structures structures and associated semantic roles.
We discuss the differences between HMEANT and HUME in \secref{sec:hmeant_comp}.

>>>>

Scalability is addressed by employing automatic and semi-automatic approximations of human
judgements. Commonly, such scores decompose over the sub-parts of
the translation, and quantify how many of these sub-parts appear in a manually created reference translation.
This decomposition allows system developers
to localize the errors.
%, or at least unconfirmed parts within the translation.
The most commonly used measures decompose over n-grams or individual words, e.g., 
BLEU \parcite{Papineni:2002}, NIST \parcite{Doddington:2002} and METEOR
\parcite{Banerjee:2005}.
Another common approach is to determine the similarity between the reference and translation
by applying string edit distance \parcite{snover2006study}.
While these measures stimulated much progress in MT research by allowing
the evaluation of massive-scale experiments, the focus on words and n-grams does
not provide a good estimate of semantic correctness, and may favour shallow string-based
MT models.

@@

Perhaps the most notable attempt at semantic MT evaluation is MEANT and
its human variant HMEANT \parcite{lo2011structured}, which quantifies the similarity between
the reference and translation in terms of the overlap in
their verbal argument structures and associated semantic roles.
We discuss the differences between HMEANT and HUME in \secref{sec:hmeant_comp}.
